---
title: "Solar and Storage Report"
author: "Andrew"
date: "2023-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Amount of Solar and Storage Stacked bar graph

```{r }

```

## Installed Solar Before and Standardized

```{r , echo=FALSE}

```

## Installed Storage Before and Standardized

```{r , echo=FALSE}

```

## Sector Bubble chart
```{r , echo=FALSE}

```

## Average amount spent Box plot

```{r , echo=FALSE}

```
The Database of State Incentives for Renewables and Efficiency (DSIRE) provides information on solar policies and incentives at the state and local levels.

Energy usage data: Energy usage can also affect the level of solar adoption in a city. https://programs.dsireusa.org/system/program/ca
link to incentives avaiable 
## 3rd party ownership rates

```{r , echo=FALSE}

```

## Most Popular installed Equipment bubble chart

```{r , echo=FALSE}

```

## Installers by City top 3

```{r , echo=FALSE}

```


## Interconnections by City

```{r , echo=FALSE}

```

## Solar EV Stacked bar graph
```{r , echo=FALSE}

```